A heterogeneous landscape of selection and epistasis in protein-coding genes revealed by two-locus statistics

### 2022-03-29 manuscript/paper.tex
getting there

Most new mutations that affect fitness are deleterious and tend to be
eliminated from a population. The amount of time that a deleterious mutation
segregates depends on the strength of selection against genomes that carry it,
with very damaging mutations kept at low frequencies and purged relatively
rapidly. In the time between mutation and fixation or loss, selected variants,
both beneficial and damaging, can dramatically impact patterns of variation in
nearby linked regions \citep[e.g.][]{Smith1974-em,Charlesworth1995-dq,Kim2000-on}.
This distortion away from neutral expectations has been empirically documented
using sequencing data from an ever-growing set of study systems, but questions
remain about the primary mode of interactions between multiple linked variants
and their joint effects on genome-wide patterns of diversity.

>>>>

Most new mutations that affect fitness are deleterious and tend to be
eliminated from a population. The amount of time that a deleterious mutation
segregates depends on the strength of selection against genomes that carry it,
with very damaging mutations kept at low frequencies and purged relatively
rapidly. In the time between mutation and fixation or loss, selected variants,
both beneficial and damaging, can dramatically impact patterns of variation in
nearby linked regions \citep[e.g.][]{Smith1974-em,Charlesworth1995-dq,Kim2000-on}.
This distortion away from neutral expectations has been empirically documented
using sequencing data from an ever-growing set of study systems
\citep{Novembre2009-kc,Cutter2013-mm,Comeron2014-oy}, but questions
remain about the primary mode of interactions between multiple linked variants
and their joint effects on genome-wide patterns of diversity.
